### 2017-04-07 paper/evaluation.tex
pass on rq5

Considering question 2, participants responded that
\emailsSequential{} of the \emailsProjectsAnswered{} projects did not
execute tests in parallel.  This mismatch is justified by cases where
neither of our checks (static or dynamic) could detect presence of
parallelism.  \Fix{elaborate} \Luis{i looked at those 6 weird
  projects, and 1 of them contains a false-negative from rq4, one of
  them considered the distributed CI server as parallelism, 2 of them
  had a custom test runner, and 2 of them implements parallelism
  inside the test (they test two+ things in one test method.}
%% did not confirmed, however,
%% the developers confirmed the need of an extra parameter at the command
%% line to execute in parallel.

>>>>

Considering question 2, participants responded that
\emailsSequential{} of the \emailsProjectsAnswered{} projects did not
execute tests in parallel.  This mismatch is justified by cases where
neither of our checks (static or dynamic) could detect presence of
parallelism.

We investigated this six projects further, and one of them contained a
false-negative result from \numRQC{}, which means that a configuration file
is compacted inside a Java container. One of them considered a
distributed CI server as parallelism. Two of those projects had a
custom JUnit test runner, which handles the parallelism itself. The
last two projects run the parallelism inside the test method, one runs
a manually created Thread to run some tests, and the other runs in
parallel by using Java 8 collection streams, that allows the
developers to iterate over a list in parallel.

%% did not confirmed, however,
%% the developers confirmed the need of an extra parameter at the command
%% line to execute in parallel.
